---
title: "IBES_CRSP_vF"
author: "Elliott Choi"
date: "12/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Library needed
```{r}
library(RPostgres)
wrds <- dbConnect(Postgres(),
                  host='wrds-pgdata.wharton.upenn.edu',
                  port=9737,
                  dbname='wrds',
                  sslmode='require',
                  user='echoi98')
library(fuzzywuzzyR)
library(tidyverse)
library(dbplyr)
library(reticulate)
library(magrittr)
```

Read in CSV File needed for comparison
```{r}
stock_database<-read.csv("IBES_to_CRSP_Linked_By_Cusip.csv",header=TRUE)
stock_database
```
Server Query CRSP Data for all companies in the file 
```{r}
res <- dbSendQuery(wrds, "select date,permno, cusip,prc, ret, vol, shrout ,hexcd from crspa.msf
                   where date between '1980-01-01'
                   and '2018-12-31' and (hexcd = 1 or hexcd=2)")
crsp_data <- dbFetch(res, n=-1)
dbClearResult(res)
crsp_data <- crsp_data %>%group_by(permno,cusip)
crsp_data
```
Organize and rearrange the data 
```{r}
crsp_data <- crsp_data %>%group_by(permno,cusip)
crsp_data <- rename(crsp_data, price= prc, monthly_returns=ret, volume = vol, shares_outstanding = shrout, exchange = hexcd)
crsp_data$market_capitalization <- crsp_data$price*crsp_data$shares_outstanding
crsp_data$exchange[which(crsp_data$exchange == "1")] = "NYSE"
crsp_data$exchange[which(crsp_data$exchange == "2")] = "AMEX"
crsp_data$year <- format(crsp_data$date,"%Y")
crsp_data$month <- format(crsp_data$date,"%m")
col_order <- c("year", "month", "permno","cusip", "price","monthly_returns","volume","shares_outstanding","market_capitalization","exchange")
crsp_data <- crsp_data[,col_order]
crsp_data
```
Filter to ensure we only have companies in both databases
```{r}
conglomerate_data <- inner_join(stock_database,crsp_data, by= c('cusip'='cusip'))
conglomerate_data <- rename(conglomerate_data, permno=permno.x, exchange=exchange.x)
col_order <- c("X","year", "month", "permno","cusip","ticker","company_name","monthly_returns","price","shares_outstanding","volume","market_capitalization","exchange")
conglomerate_data<-conglomerate_data[,col_order]
conglomerate_data
```
```{r}
conglomerate_data_cusip <- subset(stock_database, select = c('cusip'))
conglomerate_data_cusip
```

Server Query IBES Data
```{r}
res <- dbSendQuery(wrds, "select anndats,fpedats, cusip, oftic, analys, value from ibes.detu_epsus
                   where fpedats between '1980-01-01' and '2019-12-31'
                   and cusip !=''")
ibes_pull<- dbFetch(res, n=-1)
dbClearResult(res)
```
Filter the data
```{r}
ibes_pull
ibes_pull_v1<-ibes_pull
# Rename columns
ibes_pull_v1$analyst_predict_year <- format(ibes_pull_v1$anndats,"%Y")
ibes_pull_v1$analyst_predict_month <- format(ibes_pull_v1$anndats,"%m")
ibes_pull_v1$analyst_predict_year_month <- format(ibes_pull_v1$anndats,"%m-%Y")
ibes_pull_v1 <- rename(ibes_pull_v1, forecast_end_period = fpedats, analyst=analys, f_eps = value)
ibes_pull_v1<- ibes_pull_v1 %>% group_by(analyst_predict_year, analyst_predict_month,forecast_end_period,cusip)%>% mutate(number_of_estimates = n_distinct(analyst))
ibes_pull_v1 <- ibes_pull_v1 %>% filter(number_of_estimates >=3)
ibes_pull_v1$forecast_end_period_month <- format(ibes_pull_v1$forecast_end_period,"%m")
ibes_pull_v1<- ibes_pull_v1%>%filter(str_detect(forecast_end_period_month,"12"))
ibes_pull_v1
```
rename the columns we want and adjust order
```{r}
ibes_pull_v1 <- rename(ibes_pull_v1, ticker = oftic)
col_order <- c("cusip","ticker","f_eps","analyst","analyst_predict_year","analyst_predict_month","analyst_predict_year_month","forecast_end_period","number_of_estimates")
ibes_pull_v1<-ibes_pull_v1[,col_order]
ibes_pull_v1
```
Filter to ensure at least 20 data points 
```{r}
ibes_pull_v1<- ibes_pull_v1 %>% group_by(cusip)%>% mutate(number_of_periods = n_distinct(analyst_predict_year_month))
ibes_pull_v1 <- ibes_pull_v1%>% filter(number_of_periods>=20)
ibes_pull_v1
```
Filter down to make sure the size is more manageable 
```{r}
ibes_pull_v2 <- inner_join(ibes_pull_v1,conglomerate_data_cusip,by = c("cusip"="cusip"))
ibes_pull_v2
```
```{r}
ibes_pull_v2 <- arrange(ibes_pull_v2,cusip,analyst_predict_year_month)
ibes_pull_v2
```
Further Filtering
```{r}
conglomerate_data_cusip <- subset(conglomerate_data, select = c('cusip'))
conglomerate_data_cusip <- distinct(conglomerate_data_cusip)
conglomerate_data_cusip
```
```{r}
ibes_pull_v3 <- inner_join(ibes_pull_v2,conglomerate_data_cusip,by=c('cusip'='cusip'))
ibes_pull_v3 <-arrange(ibes_pull_v3,cusip,analyst_predict_year,analyst_predict_month)
ibes_pull_v3
```
Ensure that analysts records are only counted once per month 
```{r}
ibes_pull_v4<-ibes_pull_v3%>%group_by(cusip,analyst_predict_year_month)%>%distinct(analyst,.keep_all = TRUE)
col_order<- c('cusip','ticker','f_eps','analyst','analyst_predict_year','analyst_predict_month','analyst_predict_year_month',
              'forecast_end_period','number_of_estimates','number_of_periods')
ibes_pull_v4 <- ibes_pull_v4[,col_order]
ibes_pull_v4
```
Link back to original 
```{r}
conglomerate_data_v2<- inner_join(ibes_pull_v4, conglomerate_data,by = c('cusip'='cusip','analyst_predict_month'='month','analyst_predict_year'='year'))
conglomerate_data_v2
```
Filter to ensure that the data is consecutive and starts from january 
```{r}
distinct_cusip_forecast_filter <- conglomerate_data_v2 %>%group_by(cusip,analyst_predict_year,analyst_predict_month)%>%distinct(analyst_predict_year_month)
distinct_cusip_forecast_filter

temp_cusip <-''
number_of_consecutives<-0
previous_month<-0
filter_count<-0

temp_filter_file <- data.frame(matrix(ncol = 4, nrow = 0))
x <- c("analyst_predict_year_month", "cusip", "analyst_predict_year","analyst_predict_month")
colnames(temp_filter_file) <- x

for(row in 1:nrow(distinct_cusip_forecast_filter)){

  current_cusip <- distinct_cusip_forecast_filter[row,'cusip']
  # If we are on a new cusip
  if(current_cusip != temp_cusip){
    temp_cusip <- current_cusip
    # New company for us to track 
    number_of_consecutives <-0
    previous_month<-0
  }
  # If this is the start of the consecutive months
  if((distinct_cusip_forecast_filter[row,'analyst_predict_month'] =='01') & (number_of_consecutives ==0)){
    # Signals the start of counting consecutive months
    number_of_consecutives<- number_of_consecutives+1
    previous_month<-'01'
  }
  # If Feb and the previous line was month 01 (january)
  else if((distinct_cusip_forecast_filter[row,'analyst_predict_month'] =='02') & (previous_month == '01')){
    # Signals the start of counting consecutive months
    number_of_consecutives<- number_of_consecutives+1
    previous_month<-'01'
  }
  # We are already counting
  else if ((number_of_consecutives!=0))&(){

  }

}
```



